Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-09-03 ms.tex
Ran pixeltime on long darks to plot over longer timescale.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allamps.pdf}
\caption{Reference pixel time series for a two ramp integration showing pre-amplifier resets.}\label{fig:sampFig}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{allamps.pdf}
\includegraphics[width=.49\columnwidth]{allamps_long_dark.pdf}
\caption{Reference pixel time series for a two frame integration (Left) and a long dark of 108 frames. Each of the plots show the pre-amplifier resets over two different timescales.}\label{fig:sampFig}
\end{figure}
